\documentclass{article}
Cory Imel

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} San Antonio, TX
\item
  \textbf{&#149;} (720) 370-1466
\item
  \textbf{&#149;} contact@coryimel.com
\item
  \textbf{&#149;} www.linkedin.com/in/cory-imel
\end{itemize}

PROFESSIONAL EXPERIENCE

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Manager, Information Systems Security\\
United States Air Force {June 2015 - Present, San Antonio, TX}

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Led the achievement of NIST Risk Management Framework
  accreditation of an \$18M Network Attack System and a \$1.5M
  administrative system culminating in multi-year authorizations to
  operate.
\item
  \textbf{&#149;} Developed and maintained security documentation including
  system security plans, security assessment plans, risk assessment
  reports, vulnerability reports, and other organization level
  policies/procedures.
\item
  \textbf{&#149;} Ensured systems were operated, maintained, and disposed of
  in accordance with security policies and procedures as outlined in the
  security authorization package.
\item
  \textbf{&#149;} Guided a team of 4 systems administrators in the re-design,
  implementation, and maintenance of an administrative network, serving
  175 users, with \textgreater{}99.9\% core services uptime and
  \textgreater{}90\% average security configuration compliance over 2
  years.
\item
  \textbf{&#149;} Produced an Assured File Transfer standard operating
  procedure, to ensure safe manual transfer of data between
  classification levels, that was reutilized at units throughout the Air
  Force Space Command.
\item
  \textbf{&#149;} Designed the organization's data at rest
  solution/procedures utilizing Windows Bitlocker, Roxio Secure Burn,
  and SAN level encryption to meet FIPS 140-2, NIST, and DoD
  requirements 6 month ahead of the deadline.
\end{itemize}

Cyberspace Operator\\
United States Air Force {October 2014 - June 2015, San Antonio, TX}

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Operated \$18M Network Attack System to conduct offensive
  cyberspace operations against enemy communications devices.
\item
  \textbf{&#149;} Engaged in 52 network environment mapping missions,
  identifying 201 cyberspace sortie targets within assigned areas of
  operation.
\item
  \textbf{&#149;} Analyzed critical mission build tool to refactor logic
  achieving 100\% target validation accuracy.
\end{itemize}

Systems/Network Administrator\\
United States Air Force {October 2013 - October 2014, San Antonio, TX}

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Responsible for Intranet redesign, spearheading the project
  by assembling detailed research reports from government policy
  resources.
\item
  \textbf{&#149;} Re-engineered the network topology to segregate traffic
  types, and fielded a development enclave to prevent system
  availability issues and the mixing of live and training data.
\item
  \textbf{&#149;} Implemented a McAfee EPolicy Orchestrator infrastructure,
  including HIPS, Data Loss Prevention, Anti-Virus, and Policy Auditing
  to protect 25 servers and 150 endpoints from malware and data loss.
\item
  \textbf{&#149;} Identified the requirements and oversaw the migration of,
  22 Windows 2k8/2k3 servers to Windows Server 2k12 R2 including the
  migration of a Microsoft Exchange 2k3 mail server to Microsoft
  Exchange 2013.
\item
  \textbf{&#149;} Integrated 5 CentOS servers into an all Windows network to
  provide end users project management, version control, code testing,
  and trouble ticketing capabilities in order to meet overall
  configuration management requirements.
\end{itemize}

Systems/Network Administrator\\
United States Air Force {October 2009 - October 2013, Las Vegas, NV}

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Led 6 administrators responsible for maintaining \$2.7M
  Joint Worldwide Intelligence Communication Network node supporting
  24/7/365 unmanned aerial vehicle operation, and Nellis AFB exercises.
\item
  \textbf{&#149;} Created Windows 7 baseline and deployment process to
  transition 300 Windows XP clients while maintaining minimal customer
  impact.
\item
  \textbf{&#149;} Managed and configured CISCO switches, routers, and TACLANE
  IPSEC encryption devices across 31 sites including 6 WAN sites with
  99.9\% uptime SLA's.
\item
  \textbf{&#149;} Conducted patch management for 8 Windows servers while
  maintaining a \textgreater{} 99.9\% monthly uptime.
\item
  \textbf{&#149;} Assisted in the maintenance and backup of
  \textasciitilde{}82 Terabytes of combat mission data on a \$170K
  EMC/Brocade Fibre Channel system.
\end{itemize}

EDUCATION

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Bachelor of Science in Technical Studies

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Thomas Edison State University
\item
  \textbf{&#149;} Trenton, NJ
\item
  \textbf{&#149;} 102/120 Credit Hours
\end{itemize}

Associate in Applied Science in Cybersecurity

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Community College of the Air Force
\item
  \textbf{&#149;} Maxwell, AL
\item
  \textbf{&#149;} October 2016
\end{itemize}

Associate in Applied Science in Information Technology

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Community College of the Air Force
\item
  \textbf{&#149;} Maxwell, AL
\item
  \textbf{&#149;} October 2013
\end{itemize}

CERTIFICATIONS

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Cisco Certified Networking Associate Security (CCNA-Security)}
\item
  \textbf{&#149;} Jan 2017 -- Jan 2020
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Red Hat Certified Systems Administrator (RHCSA)}
\item
  \textbf{&#149;} Aug 2016 -- Aug 2019
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; GIAC Certified Incident Handler (GCIH)}
\item
  \textbf{&#149;} Sept 2014 -- Sept 2018
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; GIAC Security Essentials (GSEC)}
\item
  \textbf{&#149;} Jul 2014 -- Jul 2018
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Cisco Certified Network Associate Routing \& Switching
  (CCNA)}
\item
  \textbf{&#149;} Mar 2014 -- Jan 2020
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Comptia Security+}
\item
  \textbf{&#149;} Dec 2010 -- Jan 2021
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Comptia Network+}
\item
  \textbf{&#149;} Dec 2009 -- Jan 2021
\end{itemize}

RELEVANT COURSEWORK

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Full Stack Web Development - Java (603 Hours)\\
CodeUP &#149;~Sept 2017

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Full time hands-on and instructor led academics including,
  front-end development in HTML, CSS, JavaScript, and JQuery, as well as
  back-end development in JAVA, Spring, SQL, and cloud deployments.
\end{itemize}

Intermediate Network Warfare Training/Bridge Course (502 Hours)\\
Air Force Cyberspace Operations \textbf{&#149;} Sept 2014

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Hands-on and instructor led academics including, cyber risk
  analysis, nodal analysis, operating systems analysis, programming
  vulnerabilities, reverse engineering, forensic analysis, malware
  analysis, penetration testing, packet and log analysis, and red/blue
  teaming.
\end{itemize}

Network Management Infrastructure (192 Hours)\\
Air Force Cyberspace Operations \textbf{&#149;} Jun 2011

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Instruction on network fundamentals, OSI model, TCP/IP, lan
  switching, IPv4/IPv6 addressing, IPv4/IPv6 routing, infrastructure
  management, access control lists, NAT, and infrastructure services.
\end{itemize}

COMMUNITY INVOLVEMENT

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

CyberDEF Dojo\\
San Antonio, TX &#149; Treasurer ~&#149; Jun 2015 - Present

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Worked on the team to launch, as a not for profit
  corporation, with the goal of inculcating security and risk management
  into the culture of the greater San Antonio community through
  education and development programs.
\end{itemize}

Information Systems Security Association\\
Alamo Chapter \textbf{&#149;} Member \textbf{&#149;} Apr 2017 - Present

\begin{itemize}
\tightlist
\item
  \textbf{&#149;} Participated in local information security meet ups and
  discussions.
\end{itemize}

SKILLS

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Linux}
\item
  \textbf{&#149;} Windows
\item
  \textbf{&#149; Network Security}
\item
  \textbf{&#149;} Systems Administration
\item
  \textbf{&#149; Virtualization}
\item
  \textbf{&#149;} Scripting
\item
  \textbf{&#149; OSSIM}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Vulnerability Assessment/Management}
\item
  \textbf{&#149;} Incident Response
\item
  \textbf{&#149; Security Operations}
\item
  \textbf{&#149;} Log Correlation Engin
\item
  \textbf{&#149; Virtualization}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{&#149; Troubleshooting}
\item
  \textbf{&#149;} Communication
\item
  \textbf{&#149; JAVA}
\item
  \textbf{&#149;} JavaScript
\item
  \textbf{&#149; jQuery}
\item
  \textbf{&#149;} Splunk
\item
  \textbf{&#149; MacOS}
\end{itemize}
